### 2023-03-02 manuscript.Rmd
added submission note to front page as requested by journal

  To be submitted to: Meta-Psychology

>>>>

  Submitted to Meta-Psychology. Participate in open peer review by commenting through hypothes.is directly on this preprint. The full editorial process of all articles under review at Meta-Psychology can be found following this link: https://tinyurl.com/mp-submissions. You will find this preprint by searching for the first author’sname.
